Supplementary material to ``Estimating the Attack Ratio of Dengue Epidemics under Time-varying Force of Infection using Aggregated Notification Data''

### 2015-06-22 suppl.tex
Added section to supplementary material fixing #21. closes #21

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\bibliographystyle{naturemag}
% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}
\usepackage{url}
% Our defs 
\def \rr {$R_{t}\:$}
%opening
\title{Supplementary material to ``Estimating the Attack Ratio of Dengue 
Epidemics under Time-varying 
Force of Infection using Aggregated Notification Data''}
\author{Flavio Code\c{c}o Coelho and Luiz Max de Carvalho}

@@

>>>>

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[numbers]{natbib}
\bibliographystyle{naturemag}
% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}
\usepackage{url}
\usepackage{graphicx}
% Our defs 
\def \rr {$R_{t}\:$}
%opening
\title{Supplementary material to ``Estimating the Attack Ratio of Dengue 
Epidemics under Time-varying 
Force of Infection using Aggregated Notification Data''}
\author{Flavio Code\c{c}o Coelho and Luiz Max de Carvalho}

@@

\section*{Estimating $S_0$ from simulated data}
In order to make absolutely clear that the inference methodology proposed can 
recover the true parameter values of the underlying simulation model, we have 
devised a simple simulation experiment. Using the SIR model presented in the 
main paper we have simulated the incidence curve of the  2013 epidemic (2012 in 
table 1 of the article), using $S_0 = 0.0621$ and \rr, as estimated from the 
actual incidence data, and $\tau=1$. Figure \ref{fig:sim_data} shows the 
posterior $S$ and $I$ alongside with the simulated incidence data. It is clear 
the inference can recover the correct value for $S_0$ used to   simulate 
incidence. The script to generate the simulated data and run the inference is in 
the paper's Github repository(\verb|fit_simulated_data.py|).

\begin{figure}
 \centering
 \includegraphics[width=14cm]{./plots/Sim_DengueS2012_11_series.png}
 % Sim_DengueS2012_11_series.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{$S$ and $I$ series fitted to simulated incidence data(blue dots) 
with $S_0=0.0621$, and \rr estimated from real incidence data.}
 \label{fig:sim_data}
\end{figure}
